\documentclass{article}

\usepackage{twemojis}

\newcommand{\chalet}{Chalet dans les bois}

\title{\chalet - Essential Guest Guide}

\newcommand*{\warnsign}{\begin{LARGE}\texttwemoji{warning}\end{LARGE}}

\newcommand{\separator}{\vspace{2em}\hrule}
\newcommand*{\subhead}[2]{\noindent\textbf{#1}: {#2}\vspace{1em}}
\newcommand*{\subsubhead}[2]{\noindent\textbf{#1}: {#2}\vspace{0.25em}}
\newcommand*{\note}[1]{\textbf{Note}: {#1}}
\newcommand*{\warning}[1]{\warnsign \ \textbf{#1} \warnsign}
\begin{document}
\maketitle

Welcome to our home! Here's everything you need to know for a comfortable stay.

\separator
\section*{Arrival \& Access}

\subhead{Address} {
    423 Avenue Lafond, Chertsey, J0K 3K0.
    \\
    \note{GPS may indicate arrival early - continue to the last cottage on your left before the roundabout.}
}

\subhead{Parking} {
    Two spots available - choose between the sloped pot or level spot near the outdoor fireplace area.
    \\
    \warning{DO NOT park behind the "No Entry" sign - septic tank area.}
}

\subhead{Check-in} {4:00 PM}\\
\subhead{Check-out} {12:00 PM}\\
\subhead{Door Access} {Use your unique code.}\\
\subhead{Wifi} {Connect to the network "ChaletDansLesBois" with the password "streliski".}

\separator
\section*{Essential Amenities and Safety}
\subhead{Septic Tank} { We have a fully sealed septic tank.
    \begin{itemize}
        \item A red indicator light near the hot tub area will illuminate if the septic tank at its 80\% capacity.
        \item Please notify us immediately if you notice this warning light during your stay.
    \end{itemize}
}

\subhead{Hot Tub} { Enjoy the hot tub located on the deck. Please follow these rules:
    \begin{itemize}
        \item Shower before entering the hot tub.
        \item No glassware in the hot tub area. Use the plastic glasses provided (in the coat closet).
        \item Keep the cover on when not in use.
        \item Set the temperature to 99\textdegree F upon arrival (takes a few hours to heat up from 80\textdegree F.)
        \item \textbf{Children must be supervised at all times.}
    \end{itemize}
}

\subhead{Safety} {
    \begin{itemize}
        \item \textbf{First Aid Kit} is located in the bathroom dresser.
        \item \textbf{Fire Extinguisher} is located by the indoor fireplace.
        \item \textbf{Fire Blanket} is located in the over drawer.
    \end{itemize}
}

\subhead{Kitchen \& Supplies}
{
    \newline\newline
    \subsubhead{Provided}{Coffee, Nespresso capsules, tea, spices, cooking essentials, cleaning products, towels, toiletries.}
    \\\subsubhead{Bring}{Beach towels, sunscreen, and any personal items you may need.}
    \\\subsubhead{Equipment}{Full kitchen, washer/dryer, and outdoor propane grill.}
    \\\subsubhead{Bedding}{Clean sheets provided; extra sheets in master bedroom armoire.}
    \\\subsubhead{Miscellaneous}{Some board game are available for use.}
    \\\subsubhead{Waste and Recycling}{Fresh bags provided; extras under the kitchen sink.}
}

\subhead{Fireplaces} {
    Wood is provided for both indoor and outdoor fireplaces.
    \\\warning{Never leave a fire unattended.}
    \newline\newline
    \subsubhead{Indoor Fireplace}{
        \\Empty ashes into the black bucket between uses.
        \\Always completely extinguish the fire by closing the door and airflow vent before leaving/sleeping.
    }
    \\\subsubhead{Outdoor Fire Pit}{
        \\Check SOPFEU website for firebans first.
        \\Extinguish the fire completely before going inside/leaving.
    }
}
\section{House Rules}
\begin{itemize}
    \item No smoking inside the chalet.
    \item No shoes inside the chalet. Please leave them at the entrance.
    \item Please respect the neighbors and keep noise at a respectful level.
    \item \textbf{Quiet hours} are from 11:00 PM to 8:00 AM.
    \item \textbf{No parties are allowed.}
    \item \textbf{Fireworks are not allowed.}
    \item Dispose of trash in designated bins.
\end{itemize}

\separator
\section{Departure Checklist}
The departure procedure is simple: leave the chalet as it was upon arrival!

With the following exceptions:
\begin{itemize}
    \item \subsubhead{Sheets}{Place used sheets in the laundry hamper in the bathroom (no need to make the beds)}
    \item \subsubhead{Trash}{Empty all bins to outside containers}
    \item \subsubhead{Kitchenware}{Wash and put away all dishes, utensils, and cookware.}
    \item \subsubhead{Hot Tub}{Reset the temperature to 80\textdegree F and ensure that the cover is on.}
    \item \subsubhead{Miscellaneous}{Turn off all lights and TVs, close all windows, and set the heating to 18\textdegree C.}
    \item \subsubhead{Outdoor}{Bring cushions for outdoor seating in, cover the BBQ.}
    \item \subsubhead{Door}{Press the ``lock'' button on the keypad while pulling firmly on the door. Ensure that the door is locked before leaving.}
\end{itemize}
\warnsign \textbf{  Additional fees will apply for any damages or excessive cleaning required.}

\separator
\section{Nearby Attractions (Top picks)}
\subhead{Sainte-Marguerite-du-Lac-Masson (15 mins)}{}
\begin{itemize}
    \item \subsubhead{Plage du Lac Masson}{Municipal beach}
    \item \subsubhead{Pub Marina Masson}{Restaurant and boat rentals}
    \item \subsubhead{Cafe O'Marguerite}{Quaint cafe with local pastries}
\end{itemize}

\subhead{Chertsey}{}
\begin{itemize}
    \item \subsubhead{Parc régional de la Forêt Oureau (30 mins)} {hiking, climbing, canoeing, paddle boarding, obstacle course, biking, cross-country skiing, snowshoeing, tubing}
    \item \subsubitem{Saint Urbain Family Camp}{Swimming}
\end{itemize}

\subhead{Day Trips}{}
\begin{itemize}
    \item \subsubhead{Saint-Sauver (35 mins)}{Sommet Saint-Sauveur water slides/skiing; Shopping and dining}
    \item \subsubhead{Rawdon (25 mins)}{Arbraska adventure park, waterfalls}
    \item \subsubhead{Saint Donat (30 mins)}{Municipal beach, mountain biking trails}
\end{itemize}

\separator
\section*{}

\textbf{Have questions? } \textit{Feel free to reach out to us anytime!}\\

Enjoy your stay at \chalet!\\

Neeth, Ewa \& Eugine

\end{document}