% PAGE 1: COVER
\newcommand{\CoverWelcome}{Welcome to our forest retreat! Here's everything you need to know for a comfortable stay.}

% PAGE 2: ARRIVAL
\newcommand{\ArrivalTitle}{Arrival \& Access}
\newcommand{\ArrivalAddressLabel}{Address}
\newcommand{\ArrivalAddress}{423 Avenue Lafond, Chertsey, J0K 3K0}
\newcommand{\ArrivalGPSNote}{Note: GPS may indicate arrival early - continue to the last cottage on your left before the roundabout}
\newcommand{\ArrivalParkingLabel}{Parking}
\newcommand{\ArrivalParking}{Two spots available - choose the sloped or level spot near the outdoor fireplace area.}
\newcommand{\ArrivalSepticWarning}{DO NOT park behind the "No Entry" sign - septic tank area}
\newcommand{\ArrivalEntryLabel}{Entry}
\newcommand{\ArrivalEntry}{Use your unique door code.}
\newcommand{\ArrivalWinterNote}{During the winter, the cold air can cause the door frame to settle tightly. If the keypad blinks red after you enter your code, don't worry! Just pull the door firmly toward you and hold it there while you re-enter the code. This aligns the lock perfectly and it should click right open.}
\newcommand{\ArrivalShoesLabel}{Shoes}
\newcommand{\ArrivalShoes}{No shoes policy - leave by entrance door}
\newcommand{\ArrivalWiFiLabel}{WiFi}
\newcommand{\ArrivalWiFi}{danslesbois, password: streliski}
\newcommand{\ArrivalWiFiNote}{Cell phone reception can be unreliable at the chalet. Please save the WiFi details before arrival in case you need to contact us upon arrival.}

% PAGE 2: AMENITIES
\newcommand{\AmenitiesTitle}{Essential Amenities and Safety}
\newcommand{\AmenitiesSepticLabel}{Septic Tank}
\newcommand{\AmenitiesSepticItemOne}{Since all wastewater goes into a sealed septic tank, please be mindful of your water use.}
\newcommand{\AmenitiesSepticItemTwo}{A red indicator light near the hot tub will illuminate when the septic tank reaches 80\% capacity}
\newcommand{\AmenitiesSepticItemThree}{Please notify us immediately if you notice this warning light is on}
\newcommand{\AmenitiesHotTubLabel}{Hot Tub}
\newcommand{\AmenitiesHotTubItemOne}{Set to 99°F upon arrival (takes a few hours to heat up from 80°F)}
\newcommand{\AmenitiesHotTubItemTwo}{Keep cover on when not in use}
\newcommand{\AmenitiesHotTubItemThree}{No glass containers - use provided plastic cups}
\newcommand{\AmenitiesHotTubItemFour}{Children require adult supervision at all times}

% PAGE 3: SAFETY & KITCHEN
\newcommand{\SafetyLabel}{Safety Equipment}
\newcommand{\SafetyFirstAid}{First aid kit: bathroom dresser drawer}
\newcommand{\SafetyFireBlanket}{Fire blanket: oven drawer}
\newcommand{\SafetyExtinguisher}{Small extinguisher: entry closet}
\newcommand{\SafetyChildGates}{Child safety gates at 3rd floor stairs and 2nd bedroom}

\newcommand{\KitchenLabel}{Kitchen \& Supplies}
\newcommand{\KitchenProvidedLabel}{Provided}
\newcommand{\KitchenProvided}{Coffee, Nespresso capsules, tea, spices, cleaning products, towels, toiletries}
\newcommand{\KitchenBringLabel}{Bring}
\newcommand{\KitchenBring}{Beach towels}
\newcommand{\KitchenEquipmentLabel}{Equipment}
\newcommand{\KitchenEquipment}{Full kitchen, washer/dryer, BBQ (propane)}
\newcommand{\KitchenBeddingLabel}{Bedding}
\newcommand{\KitchenBedding}{Clean sheets provided; extras in master bedroom armoire}
\newcommand{\KitchenWasteLabel}{Waste and Recycling}
\newcommand{\KitchenWaste}{Fresh bags provided; extras under sink}

\newcommand{\FireTitle}{Fireplaces and Outdoor fires}
\newcommand{\FireIndoorLabel}{Indoor Fireplace}
\newcommand{\FireIndoorItemOne}{Wood and starters provided}
\newcommand{\FireIndoorItemTwo}{Empty ashes into black bucket between uses}
\newcommand{\FireIndoorItemThree}{Always close door and airflow before leaving/sleeping}
\newcommand{\FireOutdoorLabel}{Outdoor Fire Pit}
\newcommand{\FireOutdoorItemOne}{Check \href{https://sopfeu.qc.ca}{SOPFEU website} for fire bans first}
\newcommand{\FireOutdoorItemTwo}{Wood provided in rack}
\newcommand{\FireOutdoorItemThree}{Extinguish completely before going inside}

\newcommand{\MiscTitle}{Miscellaneous}
\newcommand{\MiscWindow}{If the primary bedroom window sticks, gently push it open after temporarily removing the net}

% PAGE 4: RULES & DEPARTURE
\newcommand{\RulesTitle}{Quiet Hours and Rules}
\newcommand{\RulesItemOne}{No parties allowed}
\newcommand{\RulesItemTwo}{Quiet hours: 11:00 PM - 8:00 AM}
\newcommand{\RulesItemThree}{Music at respectful volume only}
\newcommand{\RulesItemFour}{No fireworks}

\newcommand{\DepartureTitle}{Departure Checklist}
\newcommand{\DepartureIntro}{Our checkout process is simple - Please leave the chalet as you found it, with these additional steps:}
\newcommand{\DepartureSheetsLabel}{Sheets}
\newcommand{\DepartureSheets}{Place used sheets in the laundry hamper in the bathroom (no need to make the beds)}
\newcommand{\DepartureFridgeLabel}{Fridge}
\newcommand{\DepartureFridge}{Remove all perishable items from the fridge (please help yourself to the takeaway containers in the the kitchen)}
\newcommand{\DepartureTrashLabel}{Trash}
\newcommand{\DepartureTrash}{Empty all bins to outside containers}
\newcommand{\DepartureDishesLabel}{Dishes}
\newcommand{\DepartureDishes}{Wash and put away all used items}
\newcommand{\DepartureHotTubLabel}{Hot tub}
\newcommand{\DepartureHotTub}{Reset to 80°F (90°F in winter), replace cover}
\newcommand{\DepartureUtilitiesLabel}{Utilities}
\newcommand{\DepartureUtilities}{Turn off lights, close windows, set heat to 15°C}
\newcommand{\DepartureOutdoorLabel}{Outdoor}
\newcommand{\DepartureOutdoor}{Bring in cushions, cover BBQ}
\newcommand{\DepartureDoorLabel}{Door}
\newcommand{\DepartureDoor}{Press the keypad's lock button and pull firmly on the handle while the door locks; press the button once more---a green light means it's secured}
\newcommand{\DepartureWarning}{Excessive cleaning or damage/missing items will incur additional fees.}

% PAGE 5: ACTIVITIES
\newcommand{\ActivitiesTitle}{Nearby Activities (Top Picks)}
\newcommand{\ActivityMassonLabel}{Sainte-Marguerite-du-Lac-Masson (15 min)}
\newcommand{\ActivityMassonItemOne}{Municipal Beach du Lac Masson}
\newcommand{\ActivityMassonItemTwo}{Pub Marina Masson (boat rentals)}
\newcommand{\ActivityMassonItemThree}{Café aux Marguerites}
\newcommand{\ActivityChertseyLabel}{Chertsey}
\newcommand{\ActivityChertseyItemOne}{Parc régional de la Forêt Ouareau (hiking, canoeing, biking)}
\newcommand{\ActivityChertseyItemTwo}{Saint Urbain Family Camp (swimming)}
\newcommand{\ActivityDayTripsLabel}{Day Trips}
\newcommand{\ActivityDayTripOne}{Forêt Ouareau (30 mins): hiking, climbing, canoeing, paddle boarding, obstacle course, biking, cross-country skiing, snowshoeing, tubing}
\newcommand{\ActivityDayTripTwo}{Saint-Sauveur (35 min): Sommet Saint-Sauveur water slides/skiing}
\newcommand{\ActivityDayTripThree}{Rawdon (25 min): Arbraska adventure park, waterfalls}
\newcommand{\ActivityDayTripFour}{Saint-Donat (30 min): Municipal beach, mountain biking trails}

\newcommand{\FooterQuestions}{Have questions? Check the full house guide or contact your hosts.}
\newcommand{\FooterEnjoy}{Enjoy your stay at Chalet dans les bois!}
